Model Building

### 2020-07-20 Model_Build.Rmd
Touched up datasets

## Cleaning Google Trends Data
```{r}
# cleaning google trends data by replacing <1 with 0 and making hits numeric
# also converting to tsibble
clean_gt <- gt %>%
  mutate(date = as.character(date),
         year = as.character(year(date)),
         hits = str_replace(hits, "<1","0"),
         hits = as.numeric(hits)) %>%
  rename(team = teams) %>%
  select(-X)
```

@@

## Cleaning TV Market Size
```{r}
clean_tms <- tms %>%
  mutate_all(na_if,"") %>%
  mutate(TVMarketSize = as.numeric(gsub(",","",TVMarketSize))) %>%
  rename(team = Team)
```

## Cleaning Attendance and Revenue dataset 
```{r}
clean_ar <- ar %>%
  select(Year, Tm, Attendance, Attend.G, Est..Payroll) %>%
  mutate(Attendance = as.numeric(gsub(",","",Attendance)),
         Attend.G = as.numeric(gsub(",","",Attend.G)),
         Est..Payroll = as.numeric(str_replace_all(Est..Payroll, "[^[:alnum:]]", ""))) %>%
  rename(year = Year,
         attendance = Attendance,
         att_per_game = Attend.G,
         payroll = Est..Payroll)
```

## Cleaning Team Performance
```{r}
clean_tp <- tp %>%
  mutate(team = name, 
         year = yearID,
         team = (gsub("Anaheim Angels","Los Angeles Angels of Anaheim", team)),
         team = (gsub("Florida Marlins","Miami Marlins", team))) %>%
  select(year, team, W, L, DivWin, WCWin, LgWin, WSWin, attendance) %>%
  arrange(year, team)
```

## Combining Datasets
```{r}
combined <- left_join(clean_gt, clean_po, by = c("team", "year")) %>%
  mutate(date = yearmonth(date)) %>%
  select(-year) %>%
  as_tsibble(key = team, index = date)
```

# Building Model
```{r}
model_test <- combined %>%
  filter(team =="Chicago Cubs") %>%
  model(
    snaive = SNAIVE(hits),
    ets = ETS(hits),
    arima = ARIMA(hits)
  )
```

>>>>

## Cleaning Google Trends Data
```{r}
# cleaning google trends data by replacing <1 with 0 and making hits numeric
# also converting to tsibble
clean_gt <- gt %>%
  mutate(date = as.character(date),
         year = as.character(year(date)),
         hits = str_replace(hits, "<1","0"),
         hits = as.numeric(hits)) %>%
  rename(team = teams) %>%
  select(-X) %>%
  arrange(team)
```

@@

## Cleaning TV Market Size
```{r}
clean_tms <- tms %>%
  mutate_all(na_if,"") %>%
  mutate(TVMarketSize = as.numeric(gsub(",","",TVMarketSize))) %>%
  rename(team = Team)
```
## Cleaning Team Performance
```{r}
clean_tp <- tp %>%
  mutate(team = name, 
         year = yearID,
         team = (gsub("Anaheim Angels","Los Angeles Angels of Anaheim", team)),
         team = (gsub("Florida Marlins","Miami Marlins", team))) %>%
  select(year, team, W, L, DivWin, WCWin, LgWin, WSWin, attendance) %>%
  arrange(year, team)
```

## Cleaning Attendance and Revenue dataset 
```{r}
clean_ar <- ar %>%
  mutate(attendance = as.numeric(gsub(",","",Attendance)),
         att_per_game = as.numeric(gsub(",","",Attend.G)),
         payroll = as.numeric(str_replace_all(Est..Payroll, "[^[:alnum:]]", ""))) %>%
  rename(year = Year) %>%
  select(year, Tm, attendance, att_per_game, payroll)

clean_ar <- left_join(clean_ar, clean_tp, by = c("year", "attendance")) %>%
  select(year, team, attendance, att_per_game, payroll)
```

## Combining Datasets
```{r}
combined <- left_join(clean_gt, clean_po, by = c("team", "year")) %>%
  mutate(date = yearmonth(date)) %>%
  select(-year) %>%
  as_tsibble(key = team, index = date)

combined
```

# Building Model
```{r}
model_test <- combined %>%
  filter(team =="Chicago Cubs") %>%
  model(
    snaive = SNAIVE(hits),
    ets = ETS(hits),
    arima = ARIMA(hits)
  )

model_test$arima
```
